Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-11-20 journal-draft/ettdoc.tex
Erwin's proofreading to Section 3

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li\textsuperscript{1}\corrauth, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University\textsuperscript{1}, Swisscom (Schweiz) AG\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
%\renewcommand\Authands{ and }
%\corraddr{Communication Theory Lab
%School of Electrical Engineering, 
%KTH Royal Institute of Technology
%SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
\corraddr{Chair of Communication and Distributed Systems
Ahornstraße 55 - building E3
52074 Aachen
Germany
\\Email: li@umic.rwth-aachen.de}

@@

Clustering is the process of grouping certain users in geographic proximity into a collective.
% and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
As to wireless networks where no restriction is imposed on nodes to access the spectrum, \ie 
wireless ad-hoc, mesh networks and sensor networks, clustering the network helps to decrease the transmission power consumption~\cite{Kawadia03},  improve the routing performance~\cite{clustering_mesh_globecom2010}, or imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
%In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
For cognitive radio netowrks, the formed clusters help the participating nodes improve spectrum sensing accuracy.
Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
%Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.

In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in that cluster.
In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
In a cluster, both payload and control overheads can be transmitted on the CCs.
When one or several cluster members can not access a certain CC because primary user's activity is detected on that channel, the channel will be excluded from the set of CCs.
In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
The activity of primary users is usually unknown to the secondary users thus deemed as random to secondary users.
Consequently, a cluster which secures more CCs will be more robust to random primary user activity and anticipate a longer life expectancy. 
In this paper, the robustness of the clusters is their ability to uphold with the influence of active primary users.
The robust clustering enables more secondary users to reside in the resulting clusters when the available spectrum becomes scarcer.
%

@@

Cluster size is inherently correlated with the cluster robustness.
Given a CRN, it is obvious that getting rid of certain secondary users from a cluster may yield more CCs.
However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where more users result in more accurate sensing result~\cite{Consensus_based_clustering12}.
Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, there is usually only a small number of CCs.
Thus big cluster undermines the robustness of the cluster against primary users' activity.
Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
Cluster size also plays a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.

@@

%
%
The rest of the paper is organized as follows. 
In section~\ref{related_work}, we introduce the clustering techniques in CRN and those focusing on robustness.
The relation between this paper and work~\cite{Li11_ROSS} is elaborated.
The system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
%The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
Extensive performance evaluation is given in Section~\ref{performance}.
Our work is concluded in Section~\ref{conclusion}.

@@

The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in front of active primary users.
However, this work does not consider cluster robustness and messaging overhead during frequent re-clustering processes.
A distributed clustering scheme~\cite{LIU_TMC11_2} (denoted as SOC) is proposed, which is designed to generate clusters which  have multiple CCs.
The authors compared SOC with other schemes in terms of the average number of CCs of the formed cluster, where SOC outperforms other schemes by 50\%-100\%. 
Note that SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}. 
%The robustness of the clusters comes from the multiple CCs available for the clusters.
%SOC involves three phases of distributed executions.
In the first phase of SOC, every secondary user forms clusters with some one-hop neighbors. 
In the second and final phase, each secondary user seeks to either merge other clusters or join one of them.
The product of the number of CCs and cluster size is adopted as the metric by each secondary user in every phase. 
The drawbacks of this scheme are as follows, although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.
In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters. Although the authors claim that robustness is one goal to achieve, the minimum number of clusters is finally pursued.
%
In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under the game theoretic framework. 
Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
However, as all the other clustering schemes, this scheme does not have control over the formation of the very small or very large clusters which are not desirable.
Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open..
%

@@

We consider a set of CR users $\mathcal{N}$ and a set of primary users distributed over a given area.
A set of licensed channels $\mathcal{K}$ is available for the primary users. 
The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
CR users conduct spectrum sensing independently and sequentially on all licensed channels.\footnote{We assume that every node can detect the presence of an active primary user on each channel with certain accuracy. The spectrum availability can be validated with a certain probability of detection. Spectrum sensing/validation is out of the scope of this paper.}
We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
%On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
We assume the primary users change their operation channels slowly, thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
Due to the same reason, we omit the time index for the spectrum availability. 
As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range. 
%
Among the CR users, we denote by $\text{Nb}(i)$ the neighborhood of $i$, which consists of the CR nodes located within $i$'s transmission range.

We assume there is one dedicated control channel which is used to exchange signaling messages during the clustering process.
This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
In the following, we refer to the licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.

We give the definition of cluster in CRN as follows. 
A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The size of $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
The notations used in the system model are listed in Table~\ref{tab1}.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the cluster size which is preferred\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
$f(C)$ & the number of CCs of a cluster $C$, which is used \\
& in the problem description\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
 $|C_i|$ & size of the cluster $C_i$\\
 $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li\textsuperscript{1}\corrauth, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University\textsuperscript{1}, Swisscom (Schweiz) AG\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
%\renewcommand\Authands{ and }
%\corraddr{Communication Theory Lab
%School of Electrical Engineering, 
%KTH Royal Institute of Technology
%SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
\corraddr{Chair of Communication and Distributed Systems
Ahornstrasse 55 - building E3
52074 Aachen
Germany
\\Email: li@umic.rwth-aachen.de}

@@

Clustering is the process of grouping certain users in geographic proximity into a collective.
% and as an effective technique, it is proposed with the emergence of mobile wireless networks~\cite{gerla_97} and there has been a plethora of clustering schemes.
As to wireless networks where no restriction is imposed on nodes to access the spectrum, \ie 
wireless ad-hoc, mesh networks and sensor networks, clustering the network helps to decrease the transmission power consumption~\cite{Kawadia03},  improve the routing performance~\cite{clustering_mesh_globecom2010}, or imrove the network lifetime and coverage~\cite{Abbasi_survey_07}.
%In CRN, clusters are formed in the very beginning of the network operation, and re-formed periodically according to the dynamics of the CRN.
For cognitive radio netowrks, the formed clusters help the participating nodes improve spectrum sensing accuracy.
Besides, clusters benefit channel switching when primary users are detected by at least one secondary user in that cluster, then all the cluster members can stop payload transmissions swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
%Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.

In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in that cluster.
In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
In a cluster, both payload and control overheads can be transmitted on the CCs.
When one or several cluster members can not access a certain CC because primary user's activity is detected on that channel, the channel will be excluded from the set of CCs.
In particular, if that channel is being used for payload communication, the communication pair will stop and resume transmission on another available CC.
The activity of primary users is usually unknown to the secondary users, thus deemed as random to secondary users.
Consequently, a cluster which secures more CCs will be more robust to random primary user activities and anticipate a longer life expectancy. 
In this paper, the robustness of clusters is their ability to uphold with the influence of active primary users.
The robust clustering enables more secondary users to reside in the resulting clusters when the available spectrum becomes scarcer.
%

@@

Cluster size is inherently correlated with the cluster robustness.
Given a CRN, it is obvious that getting rid of certain secondary users from a cluster may yield more CCs.
However, this contradicts to one of the motivations of clustering, \ie the cooperative decision making, where in general more users result in more accurate sensing results~\cite{Consensus_based_clustering12}.
Thus the number of small clusters, especially the \textit{singleton clusters}, \ie the cluster which has only one CR node, should be minimized.
On the other hand, as to the cluster which consists of many nodes, although the spectrum sensing is benefited, there is usually only a small number of CCs.
Thus big cluster undermines the robustness of the cluster against primary users' activity.
Thus, the cluster robustness discussed in terms of number of CCs carries little meaning when the sizes of formed clusters are not considered.
Cluster size also plays a role in transmission power consumption, \ie cluster size affects the transmission power consumption when routing is conducted~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.

@@

%
%
The rest of the paper is organized as follows. 
In section~\ref{related_work}, we introduce the clustering techniques in CRN and those focusing on robustness.
The relation between this paper and work in~\cite{Li11_ROSS} is elaborated.
The system model and the robust clustering problem formulation are presented in Section~\ref{sec:model}. 
The centralized and distributed solutions are introduced in Section~\ref{centralized_solution} and~\ref{ross} respectively.
%The clustering problem is given through analysis and a centralized scheme is proposed in section~\ref{centralized_scheme}.
Extensive performance evaluation is given in Section~\ref{performance}.
Our work is concluded in Section~\ref{conclusion}.

@@

The authors of~\cite{Mansoor2015} propose a clustering algorithm which aims to speed up the process of re-clustering in case a cluster doesn't uphold in front of active primary users.
However, this work does not consider cluster robustness and messaging overhead during frequent re-clustering processes.
A distributed clustering scheme~\cite{LIU_TMC11_2} (denoted as SOC) is proposed, which is designed to generate clusters which  have multiple CCs.
The authors compared SOC with other schemes in terms of the average number of CCs of the formed cluster, where SOC outperforms other schemes by 50\%-100\%. 
Note that SOC's comparison schemes are designed either for ad hoc network without consideration of channel availability~\cite{Basagni99}, or for CRN but just considering connection among CR nodes~\cite{Zhao07}. 
%The robustness of the clusters comes from the multiple CCs available for the clusters.
%SOC involves three phases of distributed executions.
In the first phase of SOC, every secondary user forms clusters with some one-hop neighbors. 
In the second and final phase, each secondary user seeks to either merge other clusters or join one of them.
The product of the number of CCs and cluster size is adopted as the metric by each secondary user in every phase. 
The drawbacks of this scheme are as follows: although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.
In addition, this scheme leads to the high variance of the cluster sizes, which is not desired in certain applications as discussed in~\cite{clustering_globecom11, cluster_EW10}.
\cite{mansoor_15_cluster_robust} presents a heuristic method to form clusters. Although the authors claim that robustness is one goal to achieve, the minimum number of clusters is finally pursued.
%
In~\cite{Li11_ROSS} we propose a distributed clustering scheme ROSS (Robust Spectrum Sharing) under a game theoretic framework. 
Compared with the clustering schemes introduced above, the clusters are formed faster and the clusters possess more CCs than SOC.
However, as all the other clustering schemes, this scheme does not have control over formation of the very small or very large clusters which are not desirable.
Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against increasing activity of primary users, leaving the issue of cluster robustness open.
%

@@

We consider a set of CR users $\mathcal{N}$ and a set of primary users distributed over a given area.
A set of licensed channels $\mathcal{K}$ is available for the primary users. 
The CR users are allowed to transmit on channel $k \in \mathcal{K}$ only if no primary user is detected on channel $k$. 
CR users conduct spectrum sensing independently and sequentially on all licensed channels.\footnote{We assume that every node can detect the presence of an active primary user on each channel with certain accuracy. The spectrum availability can be validated with a certain probability of detection. Spectrum sensing/validation is out of the scope of this paper.}
We adopt the unit disk model~\cite{unitDiskModel} for both primary and CR users' transmission.
If a CR node $i$ locates within the transmission range of an active primary user $p$, $i$ is not allowed to use the channel which is being used by $p$.
%On the other hand, if $i$ is not in the transmission range of primary user $p$, $i$ can certainly not detect the presence of $p$.
We assume the primary users change their operation channels slowly, thus we omit the time index when denoting spectrum availability. 
%Thus we consider the clustering problem at some point in time given some degree of information of the availability of the control channels.
%Due to the same reason, we omit the time index for the spectrum availability. 
As the result of spectrum sensing, $K_i \subseteq \mathcal{K}$ denotes the set of available licensed channels for CR user $i$.
As the transmission range of primary users is limited and CR users have different locations, different CR users have different views of the spectrum availability, i.e., for any $i, j \in \mathcal{N}$, $K_i = K_{j}$ does not necessarily hold.
We therefore represent the network of CR nodes by a graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{i, j\} \in E$ if and only if $K_{i} \cap K_{j}\neq \emptyset$ and $d_{i,j} < r$, where $d_{i,j}$ is the distance between $i, j$ and $r$ is the radius of CR user's transmission range. 
%
Among the CR users, we denote by $\text{Nb}(i)$ the neighborhood of $i$, which consists of the CR nodes located within $i$'s transmission range.

We assume there is one dedicated control channel which is used to exchange signaling messages during the clustering process.
This control channel could be one of the ISM bands or other reserved spectrum which is exclusively used for transmitting control messages.\footnote{Actually, the control messages involved in the clustering process can also be transmitted on the available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighboring nodes establish communication on the same channel.}
Over the control channel, a secondary user $i$ can exchange its spectrum sensing result $K_i$ with all its one hop neighbors $\text{Nb}(i)$.
In the following, we refer to licensed channels as channels in general, and will explicitly mention the dedicated control channel if necessary.

We give the definition of cluster in CRN as follows. 
A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members.
The cluster head is able to communicate with any cluster member directly.
Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The size of $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
The notations used in the system model are listed in Table~\ref{tab1}.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the cluster size which is preferred\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
$f(C)$ & the number of CCs of a cluster $C$, which is used \\
& in the problem description\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
 $|C_i|$ & size of the cluster $C_i$\\
 $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
\bottomrule
\end{tabular}
\end{table}
